### 2016-09-05 Chapters/theory.tex
Context and problem statement first version, sent to Hidde and Hans

@@

{\Large
\textbf\newline{\textbf{}}
}

\section{Abstract}
Microbial physiology exhibits growth laws that relate the macromolecular composition of the cell to the growth rate.
Recent work has shown that these empirical regularities can be derived from coarse-grained models of resource allocation.
While these studies focus on steady-state growth, such conditions are rarely found in natural habitats, where microorganisms are continually challenged by environmental fluctuations.
The aim of this paper is to extend the study of microbial growth strategies to dynamical environments, using a self-replicator model.
We formulate dynamical growth maximization as an optimal control problem that can be solved using Pontryagin’s Maximum Principle.
We compare this theoretical gold standard with different possible implementations of growth control in bacterial cells.
We find that simple control strategies enabling growth-rate maximization at steady state are suboptimal for transitions from one growth regime to another, for example when shifting bacterial cells to a medium supporting a higher growth rate.
A near-optimal control strategy in dynamical conditions is shown to require information on several, rather than a single physiological variable.
Interestingly, this strategy has structural analogies with the regulation of ribosomal protein synthesis by ppGpp in the enterobacterium \textit{Escherichia coli}.
It involves sensing a mismatch between precursor and ribosome concentrations, as well as the adjustment of ribosome synthesis in a switch-like manner.
Our results show how the capability of regulatory systems to integrate information about several physiological variables is critical for optimizing growth in a changing environment.

@@

\section{Self-replicator model of resource allocation}
\label{sec:model}

@@

\section{Growth-rate maximization of the self-replicator reproduces bacterial growth laws}
\label{sec:growthlaws}

@@

\section{Biomass maximization as an optimal control problem}
\label{sec:optimalcontrolproblem}

@@

\section{Solution of the optimal control problem}
\label{sec:optimalcontrolsolution}

@@

\section{Simple feedback control strategies: exploiting information on nutrients or precursors}
\label{sec:steadystate}

@@

\section{A near-optimal feedback control strategy: exploiting information on the imbalance between precursors and the gene expression machinery}
\label{sec:strategies}

>>>>

\textit{Rather than propose a new theory or unearth a new fact, often the most important contribution a scientist can make is to discover a new way of seeing old theories or facts.} -- Richard Dawkins, \textit{The Selfish Gene}, preface to 1989 edition.

\section*{Summary of chapter \thechapter}
Microbial physiology exhibits growth laws that relate the macromolecular composition of the cell to the growth rate.
Recent work has shown that these empirical regularities can be derived from coarse-grained models of resource allocation.
While these studies focus on steady-state growth, such conditions are rarely found in natural habitats, where microorganisms are continually challenged by environmental fluctuations.
The aim of this paper is to extend the study of microbial growth strategies to dynamical environments, using a self-replicator model.
We formulate dynamical growth maximization as an optimal control problem that can be solved using Pontryagin’s Maximum Principle.
We compare this theoretical gold standard with different possible implementations of growth control in bacterial cells.
We find that simple control strategies enabling growth-rate maximization at steady state are suboptimal for transitions from one growth regime to another, for example when shifting bacterial cells to a medium supporting a higher growth rate.
A near-optimal control strategy in dynamical conditions is shown to require information on several, rather than a single physiological variable.
Interestingly, this strategy has structural analogies with the regulation of ribosomal protein synthesis by ppGpp in the enterobacterium \textit{Escherichia coli}.
It involves sensing a mismatch between precursor and ribosome concentrations, as well as the adjustment of ribosome synthesis in a switch-like manner.
Our results show how the capability of regulatory systems to integrate information about several physiological variables is critical for optimizing growth in a changing environment.

@@

@@

\subsection{Self-replicator model of resource allocation}
\label{sec:model}

@@

\subsection{Growth-rate maximization of the self-replicator reproduces bacterial growth laws}
\label{sec:growthlaws}

@@

\subsection{Biomass maximization as an optimal control problem}
\label{sec:optimalcontrolproblem}

@@

\subsection{Solution of the optimal control problem}
\label{sec:optimalcontrolsolution}

@@

\subsection{Simple feedback control strategies: exploiting information on nutrients or precursors}
\label{sec:steadystate}

@@

\subsection{A near-optimal feedback control strategy: exploiting information on the imbalance between precursors and the gene expression machinery}
\label{sec:strategies}

### 2016-09-05 titlepage.tex
Context and problem statement first version, sent to Hidde and Hans

%\Sethpageshift{???mm}   %%optionnel : à décommenter si besoin pour ajout d'espace afin de center la couvérture horizontalement (valeur par défaut est -5.5mm)
%\Setvpageshift{???mm}   %%optionnel : à décommenter si besoin pour ajout d'espace afin de center la couvérture verticalement (valeur par défaut est -15.5mm)

%\Universite{}    %%optionnel : à décommenter et à renseigenr si vous voulez changer le non d'université
%\Grade{}         %%optionnel : à décommenter et à renseigenr si vous voulez changer le grade
\Specialite{Biologie cellulaire }
\Arrete{7 Ao\^ut 2006}
\Auteur{Nils Giordano}
\Directeur{Johannes Geiselmann}
\CoDirecteur{Hidde de Jong}    %%optionnel : à décommenter et à renseigenr si présence d'un Co-directeur de thèse
\Laboratoire{Laboratoire Interdisciplinaire de Physique}
\EcoleDoctorale{Ecole doctorale Chimie et Science du Vivant}         
\Titre{Growth control in microorganisms: theoretical and experimental study by mean of self-replicator models}
%\Soustitre{}      %%optionnel : à décommenter et à renseigenr si présence d'un sous-titre de thèse
\Depot{}

% Commande pour création de nouvelles catégories dans le jury:

%\UGTNewJuryCategory{...NomDeLaCategorie...}{...Definition...}

% Exemple \UGTNewJuryCategory{UGTFamille}{Membre de la famille} que nous ajoutons dans la commande \Jury ci-dessous sous la forme \UGTFamille{Jean Rousseau}{(...titre_et_affiliation...s'il_y_en_a...)}

\Jury{
\UGTPresident{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}
%\UGTPresidente{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}

\UGTRapporteur{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}      %% 1er rapporteur
%\UGTRapporteur{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}      %% second rapporteur

\UGTExaminateur{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}     %% 1er examinateur
%\UGTExaminateur{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}     %% second examinateur
%\UGTExaminatrice{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}    %% 3ème examinateur

\UGTDirecteur{M, Johannes Geiselmann}{Professeur Université Joseph Fourier, LIPhy, Grenoble}       %% Directeur de thèse
\UGTCoDirecteur{M, Hidde de Jong}{Directeur de recherche Inria, Grenoble -- Rhône-Alpes}     %% Co-Directeur de thèse s'il y en a

\UGTInvite{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}
\UGTInvitee{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}
}

>>>>

%\Sethpageshift{-8mm}   %%optionnel : à décommenter si besoin pour ajout d'espace afin de center la couvérture horizontalement (valeur par défaut est -5.5mm)
%\Setvpageshift{0mm}   %%optionnel : à décommenter si besoin pour ajout d'espace afin de center la couvérture verticalement (valeur par défaut est -15.5mm)

%\Universite{}    %%optionnel : à décommenter et à renseigenr si vous voulez changer le non d'université
%\Grade{}         %%optionnel : à décommenter et à renseigenr si vous voulez changer le grade
\Specialite{Biologie cellulaire}
\Arrete{7 Ao\^ut 2006}
\Auteur{Nils GIORDANO}
\Directeur{Johannes GEISELMANN}
\CoDirecteur{Hidde DE JONG}
\Laboratoire{Laboratoire Interdisciplinaire de Physique}
\EcoleDoctorale{Ecole doctorale Chimie et Science du Vivant}         
\Titre{Microbial growth control in shifting environments}
\Soustitre{Theoretical and experimental study of resource allocation in \textit{Escherichia coli}}      %%optionnel : à décommenter et à renseigenr si présence d'un sous-titre de thèse
\Depot{}

% Commande pour création de nouvelles catégories dans le jury:
%\UGTNewJuryCategory{...NomDeLaCategorie...}{...Definition...}
% Exemple \UGTNewJuryCategory{UGTFamille}{Membre de la famille} que nous ajoutons dans la commande \Jury ci-dessous sous la forme \UGTFamille{Jean Rousseau}{(...titre_et_affiliation...s'il_y_en_a...)}

\Jury{
\UGTPresident{M, Olivier BERNARD}{Chargé de recherche, Inria, Nice -- Sophia-Antipolis (à confirmer pour président)}     %% 2ème examinateur
%\UGTPresidente{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}

\UGTRapporteur{M, Matthew SCOTT}{Associate Professor, Department of Applied Mathematics, University of Waterloo (CA)}      %% 1er rapporteur
\UGTRapporteur{M, Guy-Bart STAN}{Reader, Department of Bioengineering, Imperial College London (U.K.)}      %% second rapporteur

\UGTExaminateur{M, Matthieu JULES}{Chargé de recherche, Inra, Grignon}     %% 1er examinateur
\UGTExaminatrice{Mme, Irina MIHALCESCU}{Maître de conférence, Université Grenoble Alpes, LIPhy}    %% 3ème examinateur

\UGTDirecteur{M, Johannes GEISELMANN}{Professeur, Université Grenoble Alpes, LIPhy}       %% Directeur de thèse
\UGTCoDirecteur{M, Hidde DE JONG}{Directeur de recherche, Inria, Grenoble -- Rhône-Alpes}     %% Co-Directeur de thèse s'il y en a

\UGTInvite{M, Jean-Luc GOUZÉ}{Directeur de recherche, Inria, Nice -- Sophia-Antipolis}
%\UGTInvitee{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}
}
